### 2020-08-18 ms/suppmat.tex
Incorporate Geir's and Brian's suggestions
Start new pages after each table
Add changes to new epsilon methodology and Brian and Geir comments

@@

@@

@@

@@

>>>>

\subsection*{Estimation of uncertainty in return estimates based on scale data}

We incorporated the uncertainty in the conversion from size group (small and large returns) to age class (1SW and 2SW returns) by 
approximating the variance of log return abundance of each maiden age class 1SW and 2SW by assuming that the probability 
of the true number of returns of a given age, river, year, and size group ($N_{r,t,s,a}$) can be derived from a hypergeometric distribution

\begin{equation}
p[N_{r,t,s,a}|0:N_{r,t,s}] \sim Hypergeometric(n_{r,t,s}, 0:N_{r,t,s}, N_{r,t,s}:0, n_{r,t,s,a}),
\end{equation}

where $n_{r,t,s,a}$ is the number of scale samples in river r, year t, of returning age a, and of size group s;
$n_{r,t,s}$ is the total number of scale samples in river r, year t, and of size group s; and
$N_{r,t,s}$ is the total number of returns in river, year t, and of size group s.

We therefore obtain a vector of the probabilities of the returns of a given river r, year t, size group s and age a (i.e. $N_{r,t,s,a}$)
across the whole range of potential values, i.e. from zero to $N_{r,t,s}$, which provides the weighting probabilities to generate 10,000 random draws of $N_{r,t,s,a}$. 
We then add the draws of the same age from both size groups:
to obtain the estimates of number of returns of a given age a (i.e. 1SW or 2SW) for a given river and year ($N_{r,t,a}$):

\begin{equation}
N_{r,t,a} = N_{r,t,a,s=small}+ N_{r,t,a,s=large}.
\end{equation}

Lastly, as the coefficient of variation are comparable to standard deviations of less than 0.3 in the log-scale, we obtain
the estimate of $\epsilon_{r,t,a}$ as

\begin{equation}
\epsilon_{r,t,a} \approx \sigma_{log(N_{r,t,a})}.
\end{equation}

The $\epsilon_{r,t,a}$ parameter is used as the variance term in equations~8 and 9 of the manuscript.
The data used is in Table~\ref{tab:scales} while the estimates of $\epsilon_{r,t,a}$ are provided in Tables~\ref{tab:epsilon1} and~\ref{tab:epsilon2}.

There are a number of years with very few scales samples, particularly for the
Campbellton population, and one year for this population (2011) with no scales
samples. Under these conditions, the model provides high estimates of
$\epsilon$, but which are somewhat constrained by the log-transformation of
abundance draws of a uniform distribution. Thus, the value of $\epsilon$ for
2011, the year with no scale samples, is of 0.711 (Table~\ref{tab:epsilon1}),
which is likely an underestimate of true uncertainty given the absence of
data. Nonetheless, the model results in small $\epsilon$ values for years
where there are ten or more scale samples. 
For years where there are no scale nor return samples to draw inferences from (e.g. a year for which there are no small 2SW scales, nor large scale samples),
sometimes the error for 2SW returns cannot be estimated; in these cases we set the value of $\epsilon_{2}$ to 0.999.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/camp-scale-epsilon-example.png} \caption{Example
        of the estimation of $\epsilon_{1}$ for two different years of data for the Campbellton population: year 2011 where
        there were no scale samples, and year 2014 with a large number of scales samples. a) Distribution of draws of potential
    1SW abundances, adding the estimates from both small and large returns, for the year 2011. Note that the distribution spans the whole range of
returns (up to 5443). b) The same distribution but log-transformed, which results in a right-skewed distribution. The blue line represents the normal
distribution fitted to the log-transformed data, from which $\epsilon_{1}$ is equal to its standard deviation. b) Distribution of draws of potential
    1SW abundances, adding the estimates from both small and large returns, for the year 2014, which is much tightly constrained. d) The distribution
of log-transformed abundance draws for year 2014. In this case, the normal distribution fitted is much tighter and more closely resembles the underlying histogram,
and results in a much lower estimate of $\epsilon_{1}$.}
    \label{fig:priors} 
\end{figure}

\input{scales_tab.tex}

\input{epsilon1_tab.tex}

\input{epsilon2_tab.tex}

@@

\subsection*{Error in smolt abundances used in the model}

@@

\subsection*{Population-level estimates of smolt abundance}

@@

%\hspace{8em}

@@

\input{table-logitprmu.tex}

\input{table-logitprsigma.tex}
